---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all(here::here("."))
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/valid)](https://CRAN.R-project.org/package=valid)
<!-- badges: end -->

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("rappster/pops")
```

## What?

Setting and getting custom options/settings for the packages you are developing.

## Why?

I often (feel like I) need to store package specific "stuff" such as
options/settings. and always came up with custom code in the various packages I
developed -> trying to practice better "DRY".

## How?

```{r}
library(pops)
```

### Initialize package options

In your package's `.onLoad()` or `.onAttach()` function you can call

```{r eval=FALSE}
init_package_options(<pkg_name>)
```

For example 

```{r}
.onLoad <- function(libname, pkgname) {
    options(digits.secs = 3)
    Sys.setenv(TZ = "UTC")
    Sys.setenv(language = "en")

    init_package_options(
      pkg_name = pkgname, 
      values = list(hello = "world", devops_env = "staging")
    )
    invisible(TRUE)
}
```

As this function's side effects will only materialize when you load an actual package, let's try things out in a more direct manner.

If you are calling this **within** a package project (check by calling `pkg_name()`) then the following will work. 

(Otherwise, just set `pkg_name = "test"` in the following call to
`init_package_options`).

```{r}
init_package_options(values = list(hello = "world", devops_env = "staging"))
```

This created an "container environment" in your global options. It's either empty or in case you specified `values` it will contain those objects.

```{r}
(option_env_name <- options() %>% names() %>% stringr::str_subset("__.__"))
```

```{r}
(option_env <- getOption(option_env_name))
```

```{r}
option_env %>% ls()
```

```{r}
option_env$hello
```

### Get and set options

There three convenience functions to get and set options/objects within the option
environment

Return option values in a name-value list

```{r}
get_options()
```

```{r}
get_options(c("devops_env", "hello"))
```

```{r}
get_options(c("hello"))
```

Return option values

```{r}
get_option("hello")
```

Set option values

```{r}
set_options(list(devops_env = "dev", foo = "bar"))
```

```{r}
get_options()
```

